SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-05-01 scipy-1.0/paper.tex

% NOTE: some usage stats below are from https://libraries.io/pypi/scipy
% as well as github metrics; normally one doesn't put citations directly
% in abstract though (depends on field / journal)
\begin{abstract}
SciPy is an open source scientific computing library for the Python programming language.
SciPy 1.0 was released in late 2017, about 16 years after the original
version 0.1 release. SciPy
has become a \emph{de facto} standard for leveraging scientific algorithms
in the Python programming language, with more than 600
unique code contributors, millions of downloads per year, 161 dependent
packages, and 28700 dependent repositories. This includes usage of SciPy
in almost half of all machine learning projects on GitHub, and usage by
high profile projects including M87 black hole imaging and gravitational
wave analysis.
The library includes functionality spanning clustering, Fourier transforms,
integration, interpolation, file I/O, linear algebra, image processing,
orthogonal distance regression, minimization algorithms, signal processing,
sparse matrix handling, computational geometry, and statistics. In this
work, we provide an overview of the capabilities and development practices of the
SciPy library and highlight some recent technical developments.
\end{abstract}
\begin{document}

>>>>

% NOTE: some usage stats below are from https://libraries.io/pypi/scipy
% as well as github metrics; normally one doesn't put citations directly
% in abstract though (depends on field / journal)
\begin{abstract}
SciPy is an open source scientific computing library for the Python programming language.
SciPy 1.0 was released in late 2017, about 16 years after the original
version 0.1 release. SciPy
has become a \emph{de facto} standard for leveraging scientific algorithms
in the Python programming language, with more than 600
unique code contributors, millions of downloads per year, 161 dependent
packages, and 28700 dependent repositories. This includes usage of SciPy
in almost half of all machine learning projects on GitHub, and usage by
high profile projects including LIGO gravitational wave analysis and creation
of the first-ever image of a black hole (M87).
The library includes functionality spanning clustering, Fourier transforms,
integration, interpolation, file I/O, linear algebra, image processing,
orthogonal distance regression, minimization algorithms, signal processing,
sparse matrix handling, computational geometry, and statistics. In this
work, we provide an overview of the capabilities and development practices of the
SciPy library and highlight some recent technical developments.
\end{abstract}
\begin{document}
